---
title: "MY Report"
author: "Olagunju Tobi"
output:
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
library(DT)
library(readxl)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

## Testing data
The obeservation of test
```{r echo=FALSE}
mydata2<-read_xlsx("belongingdata.xlsx")
ds<-cor.test(mydata2$TotalBelonging,mydata2$AverageBelonging)
ds
summary(ds)
```
After running a correlation test between totalbelonging and age
The output provides:
1.	An explanation of what is being compared, called data in the output table.
2.	The t value: -2.6227 ; which indicate no significant of the
3.	The degree freedom: 3247 (N-1) * (C-1)
4.	The p value: 0.008763
5.	A statement of the alternative hypothesis the difference is not 0.
6.	Confidence interval is not greater than our p value

## View Table
Here is the table for our dataset human belonging a Likerscale data
```{r echo=FALSE}
datatable(mydata2, width = "100", height = "auto")
```

## Plot

```{r echo=FALSE}
ggplot(mydata2, aes(TotalBelonging)) +
  geom_density(alpha = 0.5)
plot(mydata2$TotalBelonging~mydata2$AverageBelonging, xlab = "a", ylab = "c")
```

Conclusion: We reject our result because our p value  is not up-to confidence interval which is 0.05 and hence our null hypothesis is rejected. So we can say there is relations to friendship